Report

### 2015-08-26 Report Aug 5 2015/Report Aug 2015.tex
Backup Aug 26 2015

From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise. Assume the data samples are i.i.d. Based on Maximum Likelihood (ML) principle we want to  
\begin{eqnarray}
\nonumber
maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=maximize\quad \prod_{i=1}^{l}P(\xi_{i})\\
&=maximize\quad \prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
\label{risk function1}
\end{eqnarray}
Take the logarithm of (\ref{risk function1}), we have
\begin{eqnarray}
maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),
\label{risk function2}
\end{eqnarray}
Therefore the $i$th risk function of $(\mathbf{x_{i}}, y_{i})$ can be written as 
\begin{eqnarray}
c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).
\label{risk function3}
\end{eqnarray}
Thus the equivalent formula of (12) can be written as 
\begin{equation}
minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i})),
\label{Total risk function}
\end{equation} 
In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
\begin{eqnarray}
|x|_{\epsilon}=\left\{\begin{array}{ll}
0   &if\quad |x|<\epsilon\\
|x|-\epsilon  &otherwise\\
\end{array}\right.
\label{Vepsilon}
\end{eqnarray}
Thus the cost function in $\epsilon$-SVR can be written as 
\begin{equation}
\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
\label{cost function}
\end{equation}
where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as 
\begin{equation}
minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
\label{total cost function}
\end{equation} 
where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
\begin{equation}
minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
\label{final cost function}
\end{equation}
where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
\begin{eqnarray}
\nonumber
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
s.t. \left\{\begin{array}{ll}
y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
\epsilon, \xi,\hat{\xi} &\geq 0\\
\end{array}\right.
\end{eqnarray}
where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered, we arrive to at a convex minimization problem \cite{smola and skpkof 1998a tutorial of SVR}.

we construct dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
\begin{eqnarray}
\nonumber
\min_{\mathbf{w}, \xi, \hat{\xi}} \max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
\nonumber
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right. 
\label{lagrange duality1}
\end{eqnarray}
where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, the dual problem of (\ref{lagrange duality1}) can be formulated as
\begin{eqnarray}
\nonumber
\max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\min_{\mathbf{w}, \xi, \hat{\xi}} \Theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
\nonumber
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\ 
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right.\label{lagrange duality2}
\end{eqnarray}
Karush–Kuhn–Tucker (KKT) condition is satisfied or not \cite{} determines whether a non linear optimization problem find its optimal solution, the complementary KKT solution of (\ref{lagrange duality2}) is 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{ll}
\eta_{i}\xi_{i}=0\\
\hat{\eta}_{i}\hat{\xi}_{i}=0\\
\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))=0\\
\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))=0\\
\end{array}\right.
\label{complementary KKT condition}
\end{IEEEeqnarray}

Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.

@@

\begin{equation}
\frac{\partial \theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
\label{partial2}
\end{equation}

\begin{equation}
\frac{\partial \theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
\label{partial3}
\end{equation}

\begin{equation}
\frac{\partial \theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
\label{partial4}
\end{equation} 
Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function, for sake of brevity, we make $C_{i}$ uniform to all data samples ：
\begin{eqnarray}
\nonumber
maximize\quad\Theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
\nonumber
&+&(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
+\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
&-&\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
&s.t.&\left\{\begin{array}{l}
\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
0<\alpha<C\tilde{R}^{'}(\alpha)\\
0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\
\end{array}\right.
\label{dual objective function1}
\end{eqnarray}
(\ref{dual objective function1}) can be simplified to 
\begin{eqnarray}
\nonumber
maximize\quad \Theta &=&-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
&+&C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
&=&-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{dual optimization function2}
\end{eqnarray}
where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix. We define the following $2l$ vectors 
$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
\begin{eqnarray}
\mathbf{v}_{i}=\left\{\begin{array}{ll}
1\quad i=1,\ldots, l\\
-1\quad i=l+1,\ldots, 2l\\ 
\end{array}\right.
\end{eqnarray}
(\ref{dual optimization function2}) can be reformulate as 
\newcommand{\mysmallarraydecl}{\renewcommand{%
\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
\renewcommand{\baselinestretch}{1.1}%
\settowidth{\normalbaselineskip}{\scriptsize
\hspace{\baselinestretch\baselineskip}}%
\setlength{\baselineskip}{\normalbaselineskip}%
\setlength{\jot}{0.25\normalbaselineskip}%
\setlength{\arraycolsep}{2pt}}
\begin{equation}
maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}& -\mathbf{K}\\
-\mathbf{K}& \mathbf{K}
\end{IEEEeqnarraybox*}\right]
\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{vectorize dual optimization function}
\end{equation}

@@

-\epsilon(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}

@@

\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}

@@

Fig.\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$). From Fig.\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle. On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
\section{Stopping Criteria}\label{stopping criteria}
\section{Hyperparameter Setting}
\section{Computer Simulations}

>>>>

From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise. Assume the data samples are i.i.d. Based on Maximum Likelihood (ML) principle we want to  
\begin{eqnarray}
\nonumber
maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=maximize\quad \prod_{i=1}^{l}P(\xi_{i})\\
&=maximize\quad \prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
\label{risk function1}
\end{eqnarray}
Take the logarithm of (\ref{risk function1}), we have
\begin{eqnarray}
maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),
\label{risk function2}
\end{eqnarray}
Therefore the $i$th risk function of $(\mathbf{x_{i}}, y_{i})$ can be written as 
\begin{eqnarray}
c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).
\label{risk function3}
\end{eqnarray}
Thus the equivalent formula of (12) can be written as 
\begin{equation}
minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i})),
\label{Total risk function}
\end{equation} 
In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
\begin{eqnarray}
|x|_{\epsilon}=\left\{\begin{array}{ll}
0   &if\quad |x|<\epsilon\\
|x|-\epsilon  &otherwise\\
\end{array}\right.
\label{Vepsilon}
\end{eqnarray}
Thus the cost function in $\epsilon$-SVR can be written as 
\begin{equation}
\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
\label{cost function}
\end{equation}
where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as 
\begin{equation}
minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
\label{total cost function}
\end{equation} 
where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
\begin{equation}
minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
\label{final cost function}
\end{equation}
where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
\begin{eqnarray}
\nonumber
minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
s.t. \left\{\begin{array}{ll}
y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
\epsilon, \xi,\hat{\xi} &\geq 0\\
\end{array}\right.
\label{primal objective function}
\end{eqnarray}
where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered, we arrive to at a convex minimization problem \cite{smola and skpkof 1998a tutorial of SVR}.

construct Lagrangian dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier,  dual optimization problem
\begin{eqnarray}
\nonumber
\min_{\alpha, \hat{\alpha}, \eta, \hat{\eta}, \mathbf{w}, \xi, \hat{\xi}}\Theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
\nonumber
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right. 
\label{lagrange duality1}
\end{eqnarray}
where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers.

According to Lagrangian Theorem \cite{Introduction to SVM}, the necessary condition to find the minimum of (\ref{primal objective function}) is the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$ equal to $0$,

@@

\begin{equation}
\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
\label{partial2}
\end{equation}

\begin{equation}
\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
\label{partial3}
\end{equation}

\begin{equation}
\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
\label{partial4}
\end{equation} 
Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form ：
\begin{eqnarray}
\nonumber
\theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
\nonumber
&+&(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
+\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
&-&\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
&s.t.&\left\{\begin{array}{l}
\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
0<\alpha<C\tilde{R}^{'}(\alpha)\\
0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\
\end{array}\right.
\label{dual objective function1}
\end{eqnarray}
Thus $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, according to general Lagrange function\cite{introduction to SVM}, Lagrange duality with feasible solution always less or equal to original objective function, because inequality constraints is introduced. Therefore we have $\theta\leq \Theta \leq f(\mathbf{w})$, based on the lemma 5.16 of Lagrange theorem\cite{introduction of SVM}, the upper bound of $\theta$ is given by the minimal of $f(\mathbf{w})$, equality holds only when the optimal of $f(\mathbf{w})$ is obtained (property 5.19).
Therefore the Lagrangian duality form can be written as 
\begin{eqnarray}
\nonumber
maximize\quad \Theta &=&-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
&+&C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
&=&-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{dual optimization function2}
\end{eqnarray}
where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix. We define the following $2l$ vectors 
$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
\begin{eqnarray}
\mathbf{v}_{i}=\left\{\begin{array}{ll}
1\quad i=1,\ldots, l\\
-1\quad i=l+1,\ldots, 2l\\ 
\end{array}\right.
\end{eqnarray}
(\ref{dual optimization function2}) can be reformulate as 
\newcommand{\mysmallarraydecl}{\renewcommand{%
\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
\renewcommand{\baselinestretch}{1.1}%
\settowidth{\normalbaselineskip}{\scriptsize
\hspace{\baselinestretch\baselineskip}}%
\setlength{\baselineskip}{\normalbaselineskip}%
\setlength{\jot}{0.25\normalbaselineskip}%
\setlength{\arraycolsep}{2pt}}
\begin{equation}
maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}& -\mathbf{K}\\
-\mathbf{K}& \mathbf{K}
\end{IEEEeqnarraybox*}\right]
\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{vectorize dual optimization function}
\end{equation}

@@

-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}

@@

\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}

@@

Fig.\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$). From Fig.\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle. On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
\section{Stopping Criteria}\label{stopping criteria}
As we have explained in section \ref{Introduce epsilon SVR}, the upper bound of Lagrangian dual objective function is determined by primal objective function further more the Lagrangian dual objective function equals to original objective function only when the optimal is found. Therefore, the gap between primal problem and dual problem is used to evaluate how is close is the current solution to global minimum. In our scenario, feasibility gap is employed as stopping criteria because of low computational cost and reliable performance.

Based on the dual objective function in (\ref{final complex lagrange duality}) and the primal objective function in (\ref{complex objective function1}), based on the proposition of Lagrangian theorem
 -\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})\\
+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})+\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})] \leq \frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]
\label{duality gap1}
 where $\mathbf{W}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}$. The duality gap can be obtained by 
 G(\alpha, \hat{\alpha}, \beta, \hat{\beta})=\frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]-\{-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})\\
 -\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})\\
 +\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})]\}=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha}) +(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})-Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})-Im(\mathbf{y}^{T})(\beta-\hat{\beta})+\\
 \epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{i}(\beta-\hat{\beta})+C\sum_{i=1}^{N_{r}}[\xi_{i}^{r}R^{'}(\xi_{i}^{r})+\hat{\xi}_{i}^{r}R^{'}(\hat{\xi}_{i}^{r})+\xi_{i}^{i}R^{'}(\xi_{i}^{i})+\hat{\xi}_{i}^{i}R^{'}(\hat{\xi}_{i}^{i})]
 \label{duality gap2}
Because the noise is white Gaussian, therefore the optimal risk function is 
$R(\xi)=\frac{1}{2}\xi^{2}$, $\xi$ is the slack variable, hence 
\xi R^{'}(\xi)=\xi^{2},
\label{risk functional1}
\xi_{i}^{r}(\hat{\xi}^{r})=\max(0, |Re(y_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon),
\label{risk functional2}
Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, notice $Re(y_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}$ and $Im(y_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}$ hence the last term in (\ref{duality gap2}) can be rewritten as 
C\sum_{i=1}^{N_{r}}((|\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon}+(|\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon})
\label{risk functional3}
where $()_{\epsilon}$ denotes $\epsilon$ insensitive function.
duality gap in (\ref{duality gap2}) can be divided into two part
